---
title: "Plots of Graphical Test for Discrete Uniformity and its Applications in Goodness of Fit Evaluation and Multiple Sample Comparison"
author: "Teemu Säilynoja"
output:
  html_document:
    toc: true
    toc_depth: 2
---

# Imports and data generation
```{r echo=FALSE, message=FALSE, warning=FALSE}
library(ggplot2)
library(bayesplot)
library(ggExtra)
source("ecdf_plot_functions.R")
source("eight_schools/eight_schools.data.R")
library(rstan)
library(ggpubr)
library(khroma)
theme_set(bayesplot::theme_default(base_family = "sans"))
colors <- colour("bright", names = FALSE)(4)
ggplot <- function(...) ggplot2::ggplot(...) + scale_color_bright()
theme_update(plot.title = element_text(hjust = 0.5))
```

## Set parameters for sample generation
```{r}
SEED <- 42
n <- 250
n_method_comparison <- 32
N_fig1 = 24
S_fig1 = 100
chains <- 4
mean_shift <- .2
scale_change <- .2
mean_shift_multi <- .5
scale_change_multi <- .5
plot_fsize_one_per_row <- 20
plot_fsize_two_per_row <- 22
plot_fsize_three_per_row <- 30
fig_width <- 6
fig_height <- 5

# Should the sampling and more demanding computations be done?
compute_plots = TRUE
# Should the plots be drawn?
make_plots = TRUE
# Should the plots be saved?
save <- TRUE
```

```{r}
# Pre-compute adjustment level gamma. 
if (compute_plots == TRUE){
  gamma_single <- get_gamma(n)
  gamma_multi <- get_gamma(n, chains = chains)
  gamma_SBC <- get_gamma(1000)
  gamma_1000 <- get_gamma(1000, chains = 4)
}
```

## Generate samples
```{r}
set.seed(SEED)
samples <- matrix(runif(chains*n), nrow=chains)
samples_norm <- matrix(rnorm(chains * n), nrow = chains)
large_variance <- matrix(ecdf(samples_norm[1,])(rnorm(n,0,1 + scale_change)), nrow = 1)
large_mean <- matrix(ecdf(samples_norm[1,])(rnorm(n,mean_shift,1)), nrow = 1)
shifted_chain <- samples_norm
shifted_chain[1,] <- matrix(rnorm(n,mean_shift_multi,1), nrow = 1)
scaled_chain <- samples_norm
scaled_chain[1,] <- matrix(rnorm(n,0,1 + scale_change_multi), nrow = 1)
```

# Plots
## Figure 1
```{r}
if (make_plots == TRUE) {
  set.seed(SEED)
  qdunifordered <- function(q, N, i) optimize(function(t) abs(q - 1 + pbinom(i-1, N, t)), c(0,1))$minimum
  y <- rnorm(N_fig1,0,1)
  x <- rnorm(S_fig1,0,1)
  pits <- pnorm(y,0,1)
  u <- ecdf(x)(y)
  z <- seq(0,1,length.out = N_fig1+1)
  bar_idx = 12
  
  y_hist <- ggplot() +
    geom_histogram(mapping = aes(x=y), bins = 32,
        fill = colors[1],
        colour = "black") +
        theme(
          text = element_text(size = 1.4*plot_fsize_three_per_row),
          legend.position = 'none',
          axis.ticks.y = element_blank(),
          axis.text.y = element_blank(),
          axis.line.y = element_blank()
          ) +
    labs(
      x = element_text("y"),
      y = NULL
    ) +
    scale_x_continuous(n.breaks = 4, limits=c(-3,3))
  
  x_hist <- ggplot() +
    geom_histogram(mapping = aes(x=x), bins = 32,
        fill = colors[1],
        colour = "black") +
        theme(
          text = element_text(size = 1.4*plot_fsize_three_per_row),
          legend.position = 'none',
          axis.ticks.y = element_blank(),
          axis.text.y = element_blank(),
          axis.line.y = element_blank()
          ) +
    labs(
      y = NULL,
      x = element_text("x")
    ) +
    scale_y_continuous(n.breaks = 3, limits=c(0,10)) +
    scale_x_continuous(n.breaks = 4)
  
  p_x <- ggplot(mapping = aes(x=(-90:90)/30, y=dnorm((-90:90)/30,0,1))) +
    geom_line(size = 1.2, colour = colors[1], alpha=1) +
        theme(
          text = element_text(size = 1.4*plot_fsize_three_per_row),
          legend.position = 'none',
          axis.ticks.y = element_blank(),
          axis.text.y = element_blank(),
          axis.line.y = element_blank()
          ) +
    labs(
      x = element_text("x"),
      y = NULL
    ) +
    scale_y_continuous(breaks = c()) +
    scale_x_continuous(n.breaks = 4)
  
  
  ecdf_pit <- ggplot(mapping = aes(x=pits, y = ecdf(pits)(pits))) +
    geom_step(size=1, colour = colors[1]) +
    geom_segment(
      aes(
        x = qbeta(0.025, bar_idx, N_fig1 +1 - bar_idx),
        y = bar_idx/N_fig1 , 
        xend = qbeta(0.925, bar_idx, N_fig1 + 1 - bar_idx),
        yend = bar_idx/N_fig1
        ),
      colour = colors[2],
      arrow = arrow(angle = 90, length = unit(0.02, "npc"), ends = 'both', type = 'closed'),
      size = 1.8
      ) + 
    geom_point(size=2) +
    theme(
          text = element_text(size = 1.4*plot_fsize_three_per_row),
          legend.position = 'none'
          ) +
    labs(
      y = element_text("ECDF"),
      x = element_text("u")
    ) +
    scale_y_continuous(breaks = c(0, 1), labels = c("0", "1")) +
    scale_x_continuous(breaks = c(0, .5, 1), labels = c("0", "0.5", "1"))
  
  u_u <- ggplot(mapping = aes(x=c(0,u,1), y=ecdf(u)(c(0,u,1)))) +
    geom_step(size=1, colour = colors[1]) +
    geom_segment(aes(
      x = qdunifordered(0.025, N_fig1, bar_idx),
      y = bar_idx/N_fig1 ,
      xend = qdunifordered(0.925, N_fig1, bar_idx),
      yend = bar_idx/N_fig1), colour = colors[2],
      arrow = arrow(angle = 90, length = unit(0.02, "npc"), ends = 'both', type = 'closed'),
      size = 1.8) +
        theme(
          text = element_text(size = 1.4*plot_fsize_three_per_row),
          legend.position = 'none'
          ) +
    geom_point(size=2) +
    labs(
      y = element_text("ECDF"),
      x = element_text("u")
    ) +
    scale_y_continuous(breaks = c(0, 1), labels = c("0", "1")) +
    scale_x_continuous(breaks = c(0, .5, 1), labels = c("0", "0.5", "1"))
  
  u_z <- ggplot(mapping = aes(x=z, y=ecdf(u)(z))) +
    geom_step(size=1, colour = colors[1]) +
    geom_segment(aes(x = z[bar_idx], y = qbinom(0.025, N_fig1, z[bar_idx])/N_fig1 , xend = z[bar_idx], yend = qbinom(0.925, N_fig1, z[bar_idx])/N_fig1), colour = colors[2],
      arrow = arrow(angle = 90, length = unit(0.02, "npc"), ends = 'both', type = 'closed'),
      size = 1.8) +
        theme(
          text = element_text(size = 1.4*plot_fsize_three_per_row),
          legend.position = 'none'
          ) +
    geom_point(size=2) +
    labs(
      y=element_text("ECDF"),
      x = element_text("z")
    ) +
    scale_y_continuous(breaks = c(0, 1), labels = c("0", "1")) +
    scale_x_continuous(breaks = c(0, .5, 1), labels = c("0", "0.5", "1"))
}
```

```{r}
y_hist
x_hist
p_x
ecdf_pit
u_u
u_z
```


```{r}
if (save == TRUE) {
  pdf(file="figures/normal_y_hist.pdf", width = fig_width, height = .8*fig_height)
  print(y_hist)
  dev.off()
  pdf(file="figures/normal_x_hist.pdf", width = fig_width, height = .8*fig_height)
  print(x_hist)
  dev.off()
  pdf(file="figures/normal_density.pdf", width = fig_width, height = .8*fig_height)
  print(p_x)
  dev.off()
  pdf(file="figures/ecdf_analytical_pit.pdf", width = fig_width, height = fig_height)
  print(ecdf_pit)
  dev.off()
  pdf(file="figures/ecdf_empirical_pit_u.pdf", width = fig_width, height = fig_height)
  print(u_u)
  dev.off()
  pdf(file="figures/ecdf_empirical_pit_z.pdf", width = fig_width, height = fig_height)
  print(u_z)
  dev.off()
}
```
## Figure 2
### Comparison between Aldor-Noiman and our method

```{r}
if (make_plots == TRUE) {
  an_bands <- function(n,m,alpha=.05) {
    require(future.apply)
    plan("multiprocess")
    
    c_m <- future_replicate(m, {
      y_n_sorted <- sort(runif(n))
      a_n <- pbeta(y_n_sorted, 1:n, n+1-(1:n))
      2*min(pmin(a_n,1-a_n))
    })
    gamma <- quantile(c_m,alpha)
    list(
      upper = qbeta(1-.5*gamma, 1:n, n+1-(1:n)),
      lower = qbeta(.5*gamma, 1:n, n+1-(1:n))
    )
  }
}
```


```{r}
if (make_plots == TRUE) {
  lims_ecdf_hight <- get_lims(n_method_comparison)
  lims_an <- an_bands(n_method_comparison,100000)
  p <- seq(0,1,length.out = n_method_comparison+1)
  pits <- runif(n_method_comparison)
}  
```


```{r}
if (make_plots == TRUE){
  lims_y <- data.frame(list(
    y = c(rbind(
      lims_ecdf_hight$lower/n_method_comparison,
      lims_ecdf_hight$upper/n_method_comparison)
      ), 
    idx = c(rbind(1:(n_method_comparison+1),1:(n_method_comparison+1)))))
  lims_x <- data.frame(list(
    x=c(rbind(lims_an$lower,lims_an$upper)),
    idx = c(rbind(1:n_method_comparison,1:n_method_comparison))))
  
  p_ecdf_gates <- ggplot() +
    geom_line(data = lims_y, mapping = aes(x=c(rbind(p,p)), y=y, group=idx), colour = colors[1], size = 1.2, alpha = 1) +
    geom_point(mapping = aes(x=p, y=ecdf(pits)(p)), size = 2) +
    labs(x = element_blank(), y = "ECDF", legent.text = element_blank()) +
      theme(
        text = element_text(size=plot_fsize_three_per_row),
        legend.text = element_text(size=plot_fsize_three_per_row)
      ) +
    scale_y_continuous(breaks = c(0.0,0.2,0.4,0.6,0.8, 1.0)) +
    scale_x_continuous(breaks = c(0.0,0.2,0.4,0.6,0.8, 1.0))
  
  p_an_gates <- ggplot() +
    geom_line(data = lims_x, mapping = aes(y=c(rbind(p[2:(n_method_comparison+1)],p[2:(n_method_comparison+1)])), x=x, group=idx), colour = colors[2], size = 1.2, alpha = 1) +
    geom_point(data = data.frame(pits), mapping = aes(y=p[2:(n_method_comparison+1)], x=sort(pits)), size = 2) +
    labs(x = element_blank(), y = "ECDF", legent.text = element_blank())+
      theme(
        text = element_text(size=plot_fsize_three_per_row),
        legend.text = element_text(size=plot_fsize_three_per_row)
      ) +
    scale_y_continuous(breaks = c(0.0,0.2,0.4,0.6,0.8, 1.0)) +
    scale_x_continuous(breaks = c(0.0,0.2,0.4,0.6,0.8, 1.0))
}

```

```{r}
if (save==TRUE) {
  pdf(file="figures/method_comparison_ecdf_gates.pdf", width = fig_width, height = fig_height)
  print(p_ecdf_gates)
  dev.off()
  pdf(file="figures/method_comparison_aldor-noiman_gates.pdf", width = fig_width, height = fig_height)
  print(p_an_gates)
  dev.off()
}
```


```{r}
p_ecdf_gates
p_an_gates
```


## Figure 3
### Histogram with low bin count
```{r}
if (make_plots == TRUE){
  p_uniformity_hist_20_bins <- draw_hist(samples[1,],bins = 20, fsize = plot_fsize_three_per_row)
}
if (save == TRUE) {
  pdf(file = "figures/uniformity_hist_20_bins.pdf", width = fig_width, height = fig_height)
  print(p_uniformity_hist_20_bins)
  dev.off()
}
```


```{r}
p_uniformity_hist_20_bins
```

## Histogram and ECDF plots of the uniform sample
```{r}
if (make_plots == TRUE){
    set.seed(SEED)
    p_uniformity_hist <- draw_hist(samples[1,], fsize = plot_fsize_three_per_row) + coord_cartesian(ylim = layer_scales(p_uniformity_hist_20_bins)$y$range$range)
    p_uniformity_ecdf <- unif_conf_band(pit = matrix(samples[1,], nrow=1), gamma = gamma_single) +
      theme(text = element_text(size = plot_fsize_three_per_row), legend.position = 'none') + 
      scale_x_continuous(breaks = c(0.0,0.2,0.4,0.6,0.8,1.0)) + 
      scale_y_continuous(breaks = c(0.0,0.2,0.4,0.6,0.8,1.0))
      
    p_uniformity_test_ecdf_diff <- unif_conf_band_diff(pit = matrix(samples[1,], nrow=1), gamma = gamma_single) +
      theme(text = element_text(size = plot_fsize_three_per_row), legend.position = 'none') + 
      scale_x_continuous(breaks = c(0.0,0.2,0.4,0.6,0.8,1.0)) + 
      scale_y_continuous(breaks = c(-0.1,0.0,0.1))
  }
if (save == TRUE) {
  pdf(file="figures/uniformity_hist.pdf", width = fig_width, height = fig_height)
  print(p_uniformity_hist)
  dev.off()
  pdf(file="figures/uniformity_test_ecdf.pdf", width = fig_width, height = fig_height)
  print(p_uniformity_ecdf)
  dev.off()
  pdf(file="figures/uniformity_test_ecdf_diff.pdf", width = fig_width, height = fig_height)
  print(p_uniformity_test_ecdf_diff)
  dev.off()
}
```

```{r}
p_uniformity_hist
p_uniformity_ecdf
p_uniformity_test_ecdf_diff
```





## Figure 4
### ECDF Marginal Distribution Studies
```{r}
if (make_plots == TRUE) {
  set.seed(SEED)
  lims <- data.frame(
    upper = qbinom(0.95, 250, seq(0,1,length.out = 251)),
    lower = qbinom(0.05, 250, seq(0,1,length.out = 251)))
  sampled_ecdf <- data.frame(list(x=replicate(50000, .5), y=replicate(50000, ecdf(runif(250))(.5))))
}
```

```{r}
if (make_plots == TRUE) {
  p_marg_three_xs <- ggplot(data = lims, aes(x=seq(0,1,length.out = 251))) +
    geom_line(mapping = aes(y=seq(0,1,length.out = 251)), size=.8, alpha = .7, linetype=2, color = colors[1]) +
    geom_line(mapping=aes(y=lower/250)) +
    geom_line(mapping=aes(y=upper/250)) +
    vline_at(c(0.2,0.3,0.9), color=colors[1], linetype= 2, size = 1.2) +
    geom_point(data=sampled_ecdf, aes(x=x, y=y), alpha=0) +
    labs(x = "", y = "ECDF", legent.text = element_blank()) +
      theme(
        plot.title = element_text(size=plot_fsize_two_per_row),
        text = element_text(size=plot_fsize_two_per_row),
        legend.text = element_text(size=plot_fsize_two_per_row)
      ) +
    scale_x_continuous(n.breaks = 5, breaks = c(.2,.3,.9)) +
    scale_y_continuous(breaks = c(0.0,0.2,0.4,0.6,0.8, 1.0))
  p_marg_three_xs
}
```

```{r}
if (compute_plots == TRUE) {
  set.seed(SEED)
  dt1 <- data.frame(t(replicate(100000, ecdf(runif(250))(c(.2,.3,.9)))))
}
```


```{r}
if (make_plots == TRUE){
  p12 <- ggplot(dt1, aes(x = X1, y= X2)) + geom_density_2d(n=50, colour = colors[1]) + geom_point(alpha=0) +
    labs(x = "ECDF(x = 0.2)", y = "ECDF(x = 0.3)") +
      theme(
        plot.title = element_text(size=plot_fsize_two_per_row),
        text = element_text(size=plot_fsize_two_per_row),
        legend.text = element_text(size=plot_fsize_two_per_row)
        ) +
    scale_y_continuous(breaks = c(0.2,0.3,0.4))+
    scale_x_continuous(breaks = c(0.1,0.2,0.3))
  p13 <- ggplot(dt1, aes(x = X1, y= X3)) + geom_density_2d(n=50, colour = colors[1]) + geom_point(alpha=0) +
    labs(x = "ECDF(x = 0.2)", y = "ECDF(x = 0.9)")+
      theme(
        plot.title = element_text(size=plot_fsize_two_per_row),
        text = element_text(size=plot_fsize_two_per_row),
        legend.text = element_text(size=plot_fsize_two_per_row)
      ) +
    scale_y_continuous(breaks = c(0.8,0.9,1.0)) +
    scale_x_continuous(breaks = c(0.1,0.2,0.3))
  p23 <- ggplot(dt1, aes(x = X2, y= X3)) + geom_density_2d(n=50, colour = colors[1]) + geom_point(alpha=0) +
    labs(x = "ECDF(x = 0.3)", y = "ECDF(x = 0.9)", legent.text = element_blank())+
      theme(
        plot.title = element_text(size=plot_fsize_two_per_row),
        text = element_text(size=plot_fsize_two_per_row),
        legend.text = element_text(size=plot_fsize_two_per_row)
      ) +
    scale_y_continuous(breaks = c(0.8,0.9,1.0)) +
    scale_x_continuous(breaks = c(0.2,0.3,0.4))
  p12 <- ggMarginal(p12, type="histogram", breaks = seq(0,1,length.out = 126),
      fill = "grey75",
      color = "grey50")
  p13 <- ggMarginal(p13, type="histogram", breaks = seq(0,1,length.out = 126),
      fill = "grey75",
      color = "grey50")
  p23 <- ggMarginal(p23, type="histogram", breaks = seq(0,1,length.out = 126),
      fill = "grey75",
      color = "grey50")
}
```

```{r}
p12
p13
p23
```

```{r}
if (save == TRUE){
  pdf(file="figures/ecdf_height_dependency_evaluation_points.pdf", width = fig_width, height = fig_height)
  print(p_marg_three_xs)
  dev.off()
  pdf(file="figures/ecdf_height_dependency_with_marginals_x1_x2.pdf", width = fig_width, height = fig_height)
  print(p12)
  dev.off()
  pdf(file="figures/ecdf_height_dependency_with_marginals_x1_x3.pdf", width = fig_width, height = fig_height)
  print(p13)
  dev.off()
  pdf(file="figures/ecdf_height_dependency_with_marginals_x2_x3.pdf", width = fig_width, height = fig_height)
  print(p23)
  dev.off()
}
```
## Figure 5
### Transformation to fractional ranks and the ECDF plots of the transformed samples
```{r}
demo_chains <- samples_norm
demo_chains[1,] <- scaled_chain[1,]
demo_chains[2,] <- shifted_chain[1,]
demo_transfromed <- u_scale(demo_chains)
for (chain in 1:4) {
  assign(
    paste("hist_chain_", chain,sep=""),
    ggplot(data = data.frame(X1 = demo_chains[chain, ])) + geom_histogram(
      mapping = aes(x=X1), bins = 32,
      fill = colors[chain],
      color = "black"
      ) + theme(
        text = element_text(size = 1.4*plot_fsize_three_per_row),
        legend.text = element_text(size = 1.4*plot_fsize_three_per_row),
        plot.title = element_text(size = 1.4*plot_fsize_three_per_row),
        legend.position = 'none',
        axis.ticks.y = element_blank(),
        axis.text.y = element_blank(),
        axis.line.y = element_blank()
        ) + labs(
    y = element_text(paste("Chain", chain)),
    x = if (chain != 4) {element_blank()} else {element_text("Observed value")}
    ) +
  scale_y_continuous(n.breaks = 6, limits = c(0,32)) +
  scale_x_continuous(n.breaks = 6, limits = c(-4, 4))
  )
}
for (chain in 1:4) {
  assign(
    paste("hist_tchain_", chain,sep=""),
    ggplot(data = data.frame(X1 = demo_transfromed[chain, ])) + geom_histogram(
      mapping = aes(x=X1), bins = 32,
      fill = colors[chain],
      color = "black"
      ) + theme(
        text = element_text(size = 1.4*plot_fsize_three_per_row),
        legend.text = element_text(size = 1.4*plot_fsize_three_per_row),
        plot.title = element_text(size = 1.4*plot_fsize_three_per_row),
        legend.position = 'none',
        axis.ticks.y = element_blank(),
        axis.text.y = element_blank(),
        axis.line.y = element_blank()
        ) + labs(
    y = element_blank(),
    x = if (chain != 4) {element_blank()} else {element_text("Fractional rank")}
    ) +
  scale_x_continuous(breaks = c(0, 0.5, 1), 
                     labels = c("0", "0.5", "1"))
  )
}
ecdfs_4_chains <- ggplot(
  data = reshape2::melt(apply(u_scale(demo_chains), 1, function(t) ecdf(t)(seq(0,1,length.out=n + 1)))),
  mapping = aes(x = rep(seq(0,1,length.out=n + 1), 4), y=value, color = factor(Var2), group=factor(Var2))) +
  geom_step(size=1) +
  theme(
    legend.position = 'none',
    text = element_text(size = plot_fsize_three_per_row),
    plot.title = element_text(size = plot_fsize_three_per_row),
  ) +
  labs(
    y = element_text("ECDF"),
    x = element_blank()
    ) +
  scale_y_continuous(breaks = c(0, 0.5, 1), 
                     labels = c("0", "0.5", "1")) +
  scale_x_continuous(breaks = c(0, 0.5, 1), 
                     labels = c("0", "0.5", "1")) +
  scale_color_bright()
ecdfs_diff_4_chains <- ggplot(
  data = reshape2::melt(apply(u_scale(demo_chains), 1, function(t) ecdf(t)(seq(0,1,length.out=n + 1)))), 
  mapping = aes(x = rep(seq(0,1,length.out=n + 1), 4), y=value-rep(seq(0,1,length.out=length(samples[1,]) + 1), 4), color = factor(Var2), group=factor(Var2))) +
  geom_step(size=1) +
  theme(
    legend.position = 'none',
    text = element_text(size = plot_fsize_three_per_row),
    plot.title = element_text(size = plot_fsize_three_per_row),
  ) +
  labs(
    y = element_text("ECDF difference"),
    x = element_text("Fractional rank")
    ) +
  scale_y_continuous(breaks = c(0.1,0.0,-0.1,-0.2)) +
  scale_x_continuous(breaks = c(0, 0.5, 1), 
                     labels = c("0", "0.5", "1")) +
  scale_color_bright()
hist_chain_1
hist_chain_2
hist_chain_3
hist_chain_4
hist_tchain_1
hist_tchain_2
hist_tchain_3
hist_tchain_4
ecdfs_4_chains
ecdfs_diff_4_chains
```

```{r}
if (save == TRUE) {
  for (chain in 1:4) {
    pdf(file=paste("figures/normal_chains_",chain,".pdf", sep=""), width = fig_width, height = .6*fig_height)
    nam <-paste("hist_chain_", chain, sep="")
    print(get(nam))
    dev.off()
    pdf(file=paste("figures/transformed_chains_",chain,".pdf", sep=""), width = fig_width, height = .6*fig_height)
    nam <-paste("hist_tchain_", chain, sep="")
    print(get(nam))
    dev.off()
  } 
  pdf(file="figures/ecdf_transformed_chains.pdf", width = fig_width, height = fig_height)
  print(ecdfs_4_chains)
  dev.off()
  pdf(file="figures/ecdf_diff_transformed_chains.pdf", width = fig_width, height = fig_height)
  print(ecdfs_diff_4_chains)
  dev.off()
}
```

## Figure 6
### Single sample: mean shifted
```{r}
if (make_plots == TRUE) {
  set.seed(SEED)
  p_uniformity_test_large_mean_hist <- draw_hist(large_mean[1,], fsize=plot_fsize_three_per_row)
  p_uniformity_test_large_mean_ecdf <- unif_conf_band(pit=matrix(large_mean[1,], nrow=1), gamma = gamma_single) +
      theme(
        plot.title = element_text(size=plot_fsize_three_per_row),
        text = element_text(size=plot_fsize_three_per_row),
        legend.text = element_text(size=plot_fsize_three_per_row),
        legend.position = 'none'
        ) +
    scale_y_continuous(breaks = c(0.0,0.2,0.4,0.6,0.8, 1.0)) +
    scale_x_continuous(breaks = c(0.0,0.2,0.4,0.6,0.8, 1.0))
  p_uniformity_test_large_mean_ecdf_diff <- unif_conf_band_diff(pit=matrix(large_mean[1,], nrow=1), gamma = gamma_single) +
      theme(
        plot.title = element_text(size=plot_fsize_three_per_row),
        text = element_text(size=plot_fsize_three_per_row),
        legend.text = element_text(size=plot_fsize_three_per_row),
        legend.position = 'none'
        ) +
    scale_y_continuous(n.breaks = 3) +
    scale_x_continuous(breaks = c(0.0,0.2,0.4,0.6,0.8, 1.0))
}

if (save==TRUE) {
  pdf(file="figures/uniformity_test_large_mean_hist.pdf", width = fig_width, height = fig_height)
  print(p_uniformity_test_large_mean_hist)
  dev.off()
  pdf(file="figures/uniformity_test_large_mean_ecdf.pdf", width = fig_width, height = fig_height)
  print(p_uniformity_test_large_mean_ecdf)
  dev.off()
  pdf(file="figures/uniformity_test_large_mean_ecdf_diff.pdf", width = fig_width, height = fig_height)
  print(p_uniformity_test_large_mean_ecdf_diff)
  dev.off()
}
```

```{r}
p_uniformity_test_large_mean_hist
p_uniformity_test_large_mean_ecdf
p_uniformity_test_large_mean_ecdf_diff
```

## Figure 7
### Single sample: Scaled variance
```{r}
if (make_plots == TRUE){
  set.seed(SEED)
  p_uniformity_test_large_variance_hist <- draw_hist(large_variance[1,], fsize=plot_fsize_three_per_row)
  p_uniformity_test_large_variance_ecdf <- unif_conf_band(pit=matrix(large_variance[1,], nrow=1), gamma = gamma_single) +
      theme(
        plot.title = element_text(size=plot_fsize_three_per_row),
        text = element_text(size=plot_fsize_three_per_row),
        legend.text = element_text(size=plot_fsize_three_per_row),
        legend.position = 'none'
        ) +
    scale_y_continuous(breaks = c(0.0,0.2,0.4,0.6,0.8, 1.0)) +
    scale_x_continuous(breaks = c(0.0,0.2,0.4,0.6,0.8, 1.0))
  p_uniformity_test_large_variance_ecdf_diff <- unif_conf_band_diff(pit=matrix(large_variance[1,], nrow=1), gamma = gamma_single) +
      theme(
        plot.title = element_text(size=plot_fsize_three_per_row),
        text = element_text(size=plot_fsize_three_per_row),
        legend.text = element_text(size=plot_fsize_three_per_row),
        legend.position = 'none'
        ) +
    scale_y_continuous(breaks = c(-0.1,0.0,0.1)) +
    scale_x_continuous(breaks = c(0.0,0.2,0.4,0.6,0.8, 1.0))
}
if (save==TRUE) {
  pdf(file="figures/uniformity_test_large_variance_hist.pdf", width = fig_width, height = fig_height)
  print(p_uniformity_test_large_variance_hist)
  dev.off()
  pdf(file="figures/uniformity_test_large_variance_ecdf.pdf", width = fig_width, height = fig_height)
  print(p_uniformity_test_large_variance_ecdf)
  dev.off()
  pdf(file="figures/uniformity_test_large_variance_ecdf_diff.pdf", width = fig_width, height = fig_height)
  print(p_uniformity_test_large_variance_ecdf_diff)
  dev.off()
}
```

```{r}
p_uniformity_test_large_variance_hist
p_uniformity_test_large_variance_ecdf
p_uniformity_test_large_variance_ecdf_diff
```

## Figure 8
### Eight Schools SBC
```{r echo=FALSE, message=FALSE, warning=FALSE, results="hide"}
if (compute_plots == TRUE) {
  set.seed(SEED)
  m_cp <- rstan::stan_model("eight_schools/eight_schools_cp_sbc.stan")
  x <- sbc(m_cp,  data = list(J = J, sigma = sigma, y = y), M = 1000, control = list(adapt_delta = 0.99), refresh = 0, iter = 5000, warmup = 1000)
  tau_ranks <- matrix(unlist(lapply(x$ranks, function(ranks){
    K <- length(ranks[,2])
    sum(ranks[seq(1,K,4),2])/length(ranks[seq(1,K,4),2])})), ncol = 1000)
}
```

```{r}
if (make_plots == TRUE) {
  p_8_schools_SBC_hist <- draw_hist(tau_ranks[1,], fsize=plot_fsize_three_per_row) +
      theme(
        plot.title = element_text(size=plot_fsize_three_per_row),
        text = element_text(size=plot_fsize_three_per_row),
        legend.position = "none"
        )
  p_8_schools_SBC_ecdf <- unif_conf_band(pit=tau_ranks, gamma = gamma_SBC) +
      theme(
        plot.title = element_text(size=plot_fsize_three_per_row),
        text = element_text(size=plot_fsize_three_per_row),
        legend.position = 'none'
        ) +
    scale_y_continuous(breaks = c(0.0,0.2,0.4,0.6,0.8, 1.0)) +
    scale_x_continuous(breaks = c(0.0,0.2,0.4,0.6,0.8, 1.0))
  p_8_schools_SBC_ecdf_diff <- unif_conf_band_diff(pit=tau_ranks, gamma = gamma_SBC) +
      theme(
        plot.title = element_text(size=plot_fsize_three_per_row),
        text = element_text(size=plot_fsize_three_per_row),
        legend.position = 'none'
        ) +
    scale_x_continuous(breaks = c(0.0,0.2,0.4,0.6,0.8, 1.0))
}
if (save==TRUE) {
  pdf(file="figures/p_eight_schools_SBC_hist.pdf", width = fig_width, height = fig_height)
  print(p_8_schools_SBC_hist)
  dev.off()
  pdf(file="figures/p_eight_schools_SBC_ecdf.pdf", width = fig_width, height = fig_height)
  print(p_8_schools_SBC_ecdf)
  dev.off()
  pdf(file="figures/p_eight_schools_SBC_ecdf_diff.pdf", width = fig_width, height = fig_height)
  print(p_8_schools_SBC_ecdf_diff)
  dev.off()
}
```


```{r}
p_8_schools_SBC_hist
p_8_schools_SBC_ecdf
p_8_schools_SBC_ecdf_diff
```

## Figure 10
## Multiple sample comparison: Mean shifted

```{r}
if (make_plots == TRUE){
  set.seed(SEED)
  for (idx in 1:chains) {
    nam <- paste("p_multi_chain_comparison_shifted_chain_chain" , idx, sep="")
    assign(nam, draw_hist(shifted_chain, row=idx, title=paste("Chain ", idx, sep=""), fsize = plot_fsize_three_per_row) +
      theme(
        plot.title = element_text(size=plot_fsize_three_per_row),
        text = element_text(size=plot_fsize_three_per_row),
        legend.position = "none"
        ))
  }
  p_multi_chain_comparison_shifted_chain_ecdf <- unif_conf_band(pit=shifted_chain, gamma = gamma_multi) +
      theme(
        plot.title = element_text(size=plot_fsize_three_per_row),
        text = element_text(size=plot_fsize_three_per_row),
        legend.position = "none"
        ) +
    scale_y_continuous(breaks = c(0.0,0.2,0.4,0.6,0.8, 1.0)) +
    scale_x_continuous(breaks = c(0.0,0.2,0.4,0.6,0.8, 1.0))
  p_multi_chain_comparison_shifted_chain_ecdf_diff <- unif_conf_band_diff(pit=shifted_chain, gamma = gamma_multi) +
      theme(
        plot.title = element_text(size=plot_fsize_three_per_row),
        text = element_text(size=plot_fsize_three_per_row),
        legend.position = "none"
        ) +
    scale_y_continuous(n.breaks = 3) +
    scale_x_continuous(breaks = c(0.0,0.2,0.4,0.6,0.8, 1.0))
}
if (save==TRUE) {
  for (idx in 1:chains) {
    pdf(file=paste("figures/multi_chain_comparison_shifted_chain_chain",idx,".pdf",sep=""), width = fig_width, height = fig_height)
    nam <- paste("p_multi_chain_comparison_shifted_chain_chain" , idx, sep="")
    print(get(nam))
    dev.off()
  }

pdf(file="figures/multi_chain_comparison_shifted_chain_ecdf.pdf", width = fig_width, height = fig_height)
print(p_multi_chain_comparison_shifted_chain_ecdf)
dev.off()
pdf(file="figures/multi_chain_comparison_shifted_chain_ecdf_diff.pdf", width = fig_width, height = fig_height)
print(p_multi_chain_comparison_shifted_chain_ecdf_diff)
dev.off()
}
```

```{r}
p_multi_chain_comparison_shifted_chain_chain1
p_multi_chain_comparison_shifted_chain_chain2
p_multi_chain_comparison_shifted_chain_chain3
p_multi_chain_comparison_shifted_chain_chain4
p_multi_chain_comparison_shifted_chain_ecdf
p_multi_chain_comparison_shifted_chain_ecdf_diff
```


## Figure 11
## Multiple sample comparison: Mean shifted

```{r}
if (make_plots == TRUE) {
  set.seed(SEED)
  for (idx in 1:chains) {
    nam <- paste("p_multi_chain_comparison_scaled_chain_chain" , idx, sep="")
    assign(nam, draw_hist(scaled_chain, row=idx, title=paste("Chain ", idx, sep=""), fsize = plot_fsize_three_per_row) +
      theme(
        plot.title = element_text(size=plot_fsize_three_per_row),
        text = element_text(size=plot_fsize_three_per_row),
        legend.position = "none"
        ))
  }
  p_multi_chain_comparison_scaled_chain_ecdf <- unif_conf_band(pit=scaled_chain, gamma = gamma_multi) +
      theme(
        plot.title = element_text(size=plot_fsize_three_per_row),
        text = element_text(size=plot_fsize_three_per_row),
        legend.position = "none"
        ) +
    scale_y_continuous(breaks = c(0.0,0.2,0.4,0.6,0.8, 1.0)) +
    scale_x_continuous(breaks = c(0.0,0.2,0.4,0.6,0.8, 1.0))
  p_multi_chain_comparison_scaled_chain_ecdf_diff <- unif_conf_band_diff(pit=scaled_chain, gamma = gamma_multi) +
      theme(
        plot.title = element_text(size=plot_fsize_three_per_row),
        text = element_text(size=plot_fsize_three_per_row),
        legend.position = "none"
        ) +
    scale_y_continuous(breaks = c(-0.1, 0.0, 0.1)) +
    scale_x_continuous(breaks = c(0.0,0.2,0.4,0.6,0.8, 1.0))
}

if (save==TRUE) {
  for (idx in 1:chains) {
    pdf(file=paste("figures/multi_chain_comparison_scaled_chain_chain",idx,".pdf", sep=""), width = fig_width, height = fig_height)
    nam <- paste("p_multi_chain_comparison_scaled_chain_chain" , idx, sep="")
    print(get(nam))
    dev.off()
  }

pdf(file="figures/multi_chain_comparison_scaled_chain_ecdf.pdf", width = fig_width, height = fig_height)
print(p_multi_chain_comparison_scaled_chain_ecdf)
dev.off()
pdf(file="figures/multi_chain_comparison_scaled_chain_ecdf_diff.pdf", width = fig_width, height = fig_height)
print(p_multi_chain_comparison_scaled_chain_ecdf_diff)
dev.off()
}
```

```{r}
p_multi_chain_comparison_scaled_chain_chain1
p_multi_chain_comparison_scaled_chain_chain2
p_multi_chain_comparison_scaled_chain_chain3
p_multi_chain_comparison_scaled_chain_chain4
p_multi_chain_comparison_scaled_chain_ecdf
p_multi_chain_comparison_scaled_chain_ecdf_diff
```
## Figure 13
### Chains with autocorrelation

```{r}
if (make_plots == TRUE) {
  set.seed(SEED)
  p_ar_chains_ess_per_s <- ggplot()
  for (nchains in c(2,4,8)) {
    dt <- read.csv(paste("data/mean_rejection_rate_per_ess_", nchains, "_chains.csv", sep = ""))
    p_ar_chains_ess_per_s <- p_ar_chains_ess_per_s + 
      geom_point(data = dt, mapping = aes_(x = dt$ess, y = dt$rejr, shape = factor(nchains), colour = factor(nchains))) +
      geom_line(data = dt, mapping = aes_(x = dt$ess, y = dt$rejr, colour = factor(nchains)), size = 1)
  }
  p_ar_chains_ess_per_s <- p_ar_chains_ess_per_s + 
    hline_at(
      c(0.05),
      size = c(0.2),
      linetype = 1,
      color = bayesplot:::get_color("dh")
      ) +
      labs(
        x = "ESS/S",
        y = "Rejection Rate"
      ) + theme(
      legend.position = "right",
      legend.title=element_text(),
        text = element_text(size=plot_fsize_two_per_row),
        legend.text = element_text(size=plot_fsize_two_per_row)) +
    scale_y_continuous(breaks = c(0.05,0.2,0.4,0.6,0.8, 1.0)) +
    scale_x_continuous(breaks = c(0.0,0.2,0.4,0.6,0.8, 1.0)) +
    scale_color_discrete(name = "Chains", labels = c("2", "4", "8"), type = colors) +
    scale_shape_discrete(name = "Chains", labels = c("2", "4", "8"))
}
```

```{r}
if (make_plots == TRUE) {
  set.seed(SEED)
  p_ar_chains_ess_per_ar <- ggplot()
  for (nchains in c(2,4,8)) {
    dt <- read.csv(paste("data/mean_rejection_rate_per_ar_", nchains, "_chains.csv", sep = ""))
    p_ar_chains_ess_per_ar <- p_ar_chains_ess_per_ar + 
      geom_point(data = dt, mapping = aes_(x = dt$ar, y = dt$rejr, shape = factor(nchains), colour = factor(nchains))) +
      geom_line(data = dt, mapping = aes_(x = dt$ar, y = dt$rejr, colour = factor(nchains)), size = 1)
  }
  p_ar_chains_ess_per_ar <- p_ar_chains_ess_per_ar + 
    hline_at(
      c(0.05),
      size = c(0.2),
      linetype = 1,
      color = bayesplot:::get_color("dh")
      ) +
      labs(
        x = "AR parameter value",
        y = "Rejection Rate"
      ) + theme(
      legend.position = "none",
      legend.title=element_text(),
        text = element_text(size=plot_fsize_two_per_row),
        legend.text = element_text(size=plot_fsize_two_per_row)) +
    scale_y_continuous(breaks = c(0.05, 0.2,0.4,0.6,0.8, 1.0)) +
    scale_x_continuous(breaks = c(0.0,0.2,0.4,0.6,0.8, 1.0)) +
    scale_colour_discrete(name = "Chains", labels = c("2", "4", "8"), type = colors) +
    scale_shape_discrete(name = "Chains", labels = c("2", "4", "8"))
}
```

```{r}
p_ar_chains <- ggarrange(p_ar_chains_ess_per_ar, p_ar_chains_ess_per_s, ncol=2, common.legend = TRUE, legend = "bottom")
p_ar_chains
```

```{r}
if (save==TRUE){
  pdf(file="figures/multi_chain_comparison_rej_rate_autocorrelation.pdf", width = 2*fig_width, height = fig_height)
  print(p_ar_chains)
  dev.off()
  }
```



## Figure 14 & 15
### Multiple sample comparison: Eight Schools sampling issues

```{r}
if (compute_plots == TRUE) {
  set.seed(SEED)
  fit_cp <- stan(
    file = "eight_schools/eight_schools_cp.stan",
    data = list(J = J, sigma = sigma, y = y),
    chains = 4,
    warmup = 1000,
    iter = 2000,
    cores = 4,
    seed = 483892929,
    refresh = 0,
    control = list(adapt_delta = 0.99)
  )
  chains_cp <- t(matrix(extract(fit_cp, pars = c("tau"), permuted=FALSE),ncol=4))
  
  fit_ncp <- stan(
    file = "eight_schools/eight_schools_ncp.stan",
    data = list(J = J, sigma = sigma, y = y),
    chains = 4,
    warmup = 1000,
    iter = 2000,
    cores = 4,
    seed = 483892929,
    refresh = 0,
    control = list(adapt_delta = 0.99)
  )
  
  chains_ncp <- t(matrix(extract(fit_ncp, pars = c("tau"), permuted=FALSE),ncol=4))
}
```

### Centered parameterization

```{r}
if (make_plots == TRUE){
  set.seed(SEED)
  for (idx in 1:4) {
    nam <- paste("p_eight_schools_cp_hist_" , idx, sep = "")
    assign(nam, draw_hist(chains_cp, row = idx, title = paste("Chain ", idx, sep=""), fsize = plot_fsize_three_per_row) +
      theme(
        plot.title = element_text(size=plot_fsize_three_per_row),
        text = element_text(size=plot_fsize_three_per_row),
        legend.position = "none"
        ))
  }
  p_eight_schools_cp_ecdf <- unif_conf_band(pit=chains_cp, gamma = gamma_1000)  +
      theme(
        plot.title = element_text(size=plot_fsize_three_per_row),
        text = element_text(size=plot_fsize_three_per_row),
        legend.position = "none"
        ) +
    scale_y_continuous(breaks = c(0.0,0.2,0.4,0.6,0.8, 1.0)) +
    scale_x_continuous(breaks = c(0.0,0.2,0.4,0.6,0.8, 1.0))
  p_eight_schools_cp_ecdf_diff <- unif_conf_band_diff(pit=chains_cp, gamma = gamma_1000) +
      theme(
        plot.title = element_text(size=plot_fsize_three_per_row),
        text = element_text(size=plot_fsize_three_per_row),
        legend.position = "none"
        ) +
    scale_y_continuous(breaks = c(-0.05, 0.0, 0.05)) +
    scale_x_continuous(breaks = c(0.0,0.2,0.4,0.6,0.8, 1.0))
}
if (save==TRUE) {
  for (idx in 1:4) {
    pdf(file=paste("figures/eight_schools_cp_hist_",idx,".pdf",sep=""), width = fig_width, height = fig_height)
    nam <- paste("p_eight_schools_cp_hist_" , idx, sep="")
    print(get(nam))
    dev.off()
  }

  pdf(file="figures/eight_schools_cp_ecdf.pdf", width = fig_width, height = fig_height)
  print(p_eight_schools_cp_ecdf)
  dev.off()
  pdf(file="figures/eight_schools_cp_ecdf_diff.pdf", width = fig_width, height = fig_height)
  print(p_eight_schools_cp_ecdf_diff)
  dev.off()
}
```

```{r}
p_eight_schools_cp_hist_1
p_eight_schools_cp_hist_2
p_eight_schools_cp_hist_3
p_eight_schools_cp_hist_4
p_eight_schools_cp_ecdf
p_eight_schools_cp_ecdf_diff
```

### Non-centered parameterization

```{r}
if (make_plots == TRUE){
  set.seed(SEED)
  for (idx in 1:4) {
    nam <- paste("p_eight_schools_ncp_hist_" , idx, sep = "")
    assign(nam, draw_hist(chains_ncp, row = idx, title = paste("Chain ", idx, sep=""), fsize = plot_fsize_three_per_row) +
      theme(
        plot.title = element_text(size=plot_fsize_three_per_row),
        text = element_text(size=plot_fsize_three_per_row),
        legend.position = "none"
        ))
  }
  p_eight_schools_ncp_ecdf <- unif_conf_band(pit=chains_ncp, gamma = gamma_1000) +
      theme(
        plot.title = element_text(size=plot_fsize_three_per_row),
        text = element_text(size=plot_fsize_three_per_row),
        legend.position = "none"
        ) +
    scale_y_continuous(breaks = c(0.0,0.2,0.4,0.6,0.8, 1.0)) +
    scale_x_continuous(breaks = c(0.0,0.2,0.4,0.6,0.8, 1.0))
  p_eight_schools_ncp_ecdf_diff <- unif_conf_band_diff(pit=chains_ncp, gamma = gamma_1000) +
      theme(
        plot.title = element_text(size=plot_fsize_three_per_row),
        text = element_text(size=plot_fsize_three_per_row),
        legend.position = "none"
        ) +
    scale_y_continuous(breaks = c(-0.05, 0.0, 0.05)) +
    scale_x_continuous(breaks = c(0.0,0.2,0.4,0.6,0.8, 1.0))
}
if (save == TRUE) {
  for (idx in 1:4) {
    pdf(file=paste("figures/eight_schools_ncp_hist_",idx,".pdf",sep=""), width = fig_width, height = fig_height)
    nam <- paste("p_eight_schools_ncp_hist_" , idx, sep="")
    print(get(nam))
    dev.off()
  }

  pdf(file="figures/eight_schools_ncp_ecdf.pdf", width = fig_width, height = fig_height)
  print(p_eight_schools_ncp_ecdf)
  dev.off()
  pdf(file="figures/eight_schools_ncp_ecdf_diff.pdf", width = fig_width, height = fig_height)
  print(p_eight_schools_ncp_ecdf_diff)
  dev.off()
}
```

```{r}
p_eight_schools_ncp_hist_1
p_eight_schools_ncp_hist_2
p_eight_schools_ncp_hist_3
p_eight_schools_ncp_hist_4
p_eight_schools_ncp_ecdf
p_eight_schools_ncp_ecdf_diff
```



